### 2021-02-16 Chapter-1/Chapter-1.tex
update

To address Problem 2, we make the following contributions on quantifying side-channel leakages:

\begin{itemize}
    \item We propose a method that can quantify fine-grained leaked
    information from side-channel vulnerabilities that result from actual attack
    scenarios in a single trace attack. Our approach differs from previous ones in that we
    model real attack scenarios for one execution. 
    We model the information quantification problem as a counting problem 
    and use a Monte Carlo sampling method to estimate the information leakage.
    \item We implement the method into a tool and apply it
    to several pieces of real software. \tool{} successfully identifies
    previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. 
    Our results are useful in practice.
    The leakage estimates and the corresponding trigger inputs can 
    help developers to triage and fix the vulnerabilities.
    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically. Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. The method can combine multiple leakage sites to retrieve more information as well.
    \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. We propose a method that can estimate the lower bound of information leakages. The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
\end{itemize}

>>>>

To address Problem 2, we make the following contributions on quantifying side-channel leakages in a single trace attack:

\begin{itemize}
    \item We propose a method that can quantify fine-grained leaked
    information from side-channel vulnerabilities that result from actual attack
    scenarios in a single trace attack. Our approach differs from previous ones in that we
    model real attack scenarios for one execution. 
    We model the information quantification problem as a counting problem 
    and use a Monte Carlo sampling method to estimate the information leakage.
    \item We implement the method into a tool and apply it
    to several pieces of real software. \tool{} successfully identifies
    previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. 
    Our results are useful in practice.
    The leakage estimates and the corresponding trigger inputs can 
    help developers to triage and fix the vulnerabilities.
\end{itemize}

To address Problem 2, we make the following contributions on quantifying side-channel leakages on chosen plaintext side-channel attacks: 
\begin{itemize}
    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically. Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. The method can combine multiple leakage sites to retrieve more information as well.
    \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. We propose a method that can estimate the lower bound of information leakages. The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
\end{itemize}
